---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: ../syllabus_template.tex
geometry: margin=1in

title: "Sigla 000: Curso"
author: Profesor
date: "2020/02"

email: "email"
web: "website"
webname: "webname"
officehours: "Horario"
office: "Oficina"
classroom: "*online*"
classhours: "Horario Clases"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='_cache/')
knitr::opts_chunk$set(warning=F, message=F)
# knitr::opts_knit$get(kable.force.latex = TRUE)
```



```{r dates_bib, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2020-09-07")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%d/%m")
 tfri <- format(tfri, format="%d/%m")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Semana ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
#library(knitcitations)
#library(rcrossref)
bib <- ReadBib("master.bib")
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

```

# Descripción de la asignatura

Descripción.

# Objectivos del curso

1. Objetivo 1

2. Objetivo 2

3. Objetivo 3

# Bibliografía principal

```{r, echo = FALSE, results="asis"} 
bib["vasquez2009twp", "wagner2007ws"]
``` 


# Reglamento

Reglamento

## Evaluaciones

- **20%** Prueba 1.

- **20%** Prueba 2.

## Asistencia

Reglamento asistencia

## Correos

Reglamentos correo

1. correo 1
2. correo 2


\newpage

# Horario de clases

Students must read the following before Tuesday's class session.  Important: class readings are subject to change, contingent on mitigating circumstances and the progress we make as a class.  Students are encouraged to attend lectures and check the course website for updates. 

## `r advdate(mon, 1)`: Presentación de la asignatura

## `r advdate(mon, 2)`: The First Topic Where We Read John Vasquez

```{r, echo = FALSE, results="asis"} 
bib[author = "vasquez"]
``` 

## `r advdate(mon, 3)`: The First Topic Where We Read John Vasquez

```{r, echo = FALSE, results="asis"} 
bib[author = "vasquez"]
``` 
